The French Covid-19 vaccination policy did not solve vaccination inequities: a nationwide longitudinal study on 64.5 million individuals

### 2022-05-31 ms/ms.Rmd
reorder sectios
change citation style

---
title: "The French Covid-19 vaccination policy did not solve vaccination inequities: a nationwide longitudinal study on 64.5 million individuals"
author: "F. Débarre, E. Lecoeur, L. Guimier, M. Jauffret-Roustide, A.-S. Jannot"
output:
  bookdown::pdf_document2:
    keep_tex: yes
    latex_engine: pdflatex
    includes:
      in_header: template.tex
    fig_caption: yes
    number_sections: no
    toc: no
  bookdown::html_document2:
    self_contained: no
    keep_md: true
    number_sections: no
  bookdown::word_document2: 
    number_sections: no
bibliography: VaccinationInequalities.bib
---

@@

>>>>

---
title: "The French Covid-19 vaccination policy did not solve vaccination inequities: a nationwide longitudinal study on 64.5 million individuals"
author: "F. Débarre, E. Lecoeur, L. Guimier, M. Jauffret-Roustide, A.-S. Jannot"
output:
  bookdown::word_document2: 
    number_sections: no
    toc: no
  bookdown::html_document2:
    self_contained: no
    keep_md: true
    number_sections: no
  bookdown::pdf_document2:
    keep_tex: yes
    latex_engine: pdflatex
    includes:
      in_header: template.tex
    fig_caption: yes
    number_sections: no
    toc: no
bibliography: VaccinationInequalities.bib
csl: vancouver.csl
---

@@

\newpage
